Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-10-08 manuscript/manuscript.qmd
Fix missing word

Derogations have some protective effect against more bureaucratic forms of human rights abuses and less against practical abuses (see @fig-preds-mfx-human-rights). There is no measurable difference in the probability of violating non-derogable rights across derogating- and non-derogating-countries across the entire sample. However, in first 15 months of the pandemic, derogating countries were 4–5 percentage points more likely (`r hr_mfx$discriminatory_policy.None.max$p_gt`) to have no discriminatory policies than those that did not derogate, though the difference disappears by June 2021. The next most probable outcomes—minor and moderate levels of discriminatory policies—are equally likely regardless of derogation status. Thus, contrary to our expectations, derogating states also violate non-derogable rights and implement some discriminatory policies. These findings can perhaps be attributed to increased domestic and international monitoring—since derogating states open themselves up to such monitoring and review by the UNHRC, we may be more likely to observe discrimination and non-derogable rights violations than we would in non-derogating states.

>>>>

Derogations have some protective effect against more bureaucratic forms of human rights abuses and less against practical abuses (see @fig-preds-mfx-human-rights). There is no measurable difference in the probability of violating non-derogable rights across derogating- and non-derogating-countries across the entire sample. However, in the first 15 months of the pandemic, derogating countries were 4–5 percentage points more likely (`r hr_mfx$discriminatory_policy.None.max$p_gt`) to have no discriminatory policies than those that did not derogate, though the difference disappears by June 2021. The next most probable outcomes—minor and moderate levels of discriminatory policies—are equally likely regardless of derogation status. Thus, contrary to our expectations, derogating states also violate non-derogable rights and implement some discriminatory policies. These findings can perhaps be attributed to increased domestic and international monitoring—since derogating states open themselves up to such monitoring and review by the UNHRC, we may be more likely to observe discrimination and non-derogable rights violations than we would in non-derogating states.
